---
title: "Data import"
output: github_document
---

```{r, echo = FALSE}
library(tidyverse)
```

## Data Import: CSVs

Let's import data using the `readr` package and use a relative path to load data from local file. Use clean names function of janitor package to clean up my dataset.

```{r}
litters_df = read_csv("data/FAS_litters.csv")
litters_df = janitor::clean_names(litters_df)
``` 

Now, let's start looking at/inspecting the data.

```{r}
litters_df
head(litters_df)
tail(litters_df)
```

Use view to open separate window with entire dataset. Need to use `eval = FALSE` for code to knit successfully. 

```{r, eval = FALSE}
View(litters_df)
```

skim function from `skimr` package is nice way to get quick summary of entire dataset.
```{r}
skimr::skim(litters_df)
```

Treat empty rows, NA, 999, 88 all as missing observations(via collection)
```{r, eval = FALSE}
read_csv("data/FAS_litters.csv", na = c("", "NA", 999, 88))
```

If need to skip first two rows because it has info I don't want to run:
```{r, eval = FALSE}
read_csv("data/FAS_litters.csv", na = c("", "NA", 999, 88), skip = 2)
```

Column types — can see different variable types in tibble print-out option: 

* "chr" is character variable (combination of letters and numbers) 
* "dlbl" is double variable (all numbers)

## Other file formats
